To boldly go where no science...

### 2016-05-03 nyu-data-science-reproducibility-16/be-bold.Rmd
update README, add ? to release levels fig

- Replications can fail due to methodological differences
- Methods sections don't always report essential details
- **Video captures and preserves it**

## **Essentials** for a reproducible behavioral science

@@

>>>>

- Replications can fail due to methodological differences
- Methods sections can't possibly report essential details
- **Video captures and preserves it**

<div class="centered">
<video width="640" height="480" controls>
  <source src="https://nyu.databrary.org/slot/9855/0,85147/asset/38977/download?inline=true" type="video/mp4">
Your browser does not support the video tag.
</video>

## A reproducible behavioral science *must*...

@@

<iframe src="http://databrary.org" width=640px height=400px>
</iframe>
